Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-08-14 sm.tex
[sm] add frequencies

@@

  \begin{tabular}{|c|c|c|c|c|}

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-8&80&$2\pi\times14$&\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-8&80&$2\pi\times14$&\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-5&60&$2\pi\times14$&\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-5&60&$2\pi\times14$&\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-5&90&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-5&90&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-1&60&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-1&60&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline

>>>>

$\delta'$ is the two photon detuning relative to the zero field HF splitting
of $1.7716261288(10)$GHz.
All of the relative detunings are negetive indicating that the frequency difference is smaller
than the zero field HF splitting.
A more negative number corresponds to lower order cooling sidebands
and a more negative number corresponds to higher order ones.
$\delta'_0$ the relative detuning for the carrier with the specific powers in the Raman beams.

@@

  \begin{tabular}{|c|c|c|c|c|c|c|}

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline

@@

    Axis&Order&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
